---
title: "Spatial studies of genetic diversity within species"
author: "Pierre-Edouard GUERIN, Stephanie MANEL, EPHE, CNRS"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{map_marine}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---



## Prerequisites

```{r setup}
library(rgeogendiv)
```




## BOLD dataset

**BOLD** (Barcode Of Life Database) is a database of Barcode DNA sequences of georeferenced specimen that closely approximate species.

We use the package `bold` to download a set of georeferenced sequences for the *Pomacanthidae* taxon order request.

```{r}
library(bold)
taxonRequest <- "Pomacanthidae"
resBold <- bold::bold_seqspec(taxon=taxonRequest, sepfasta=TRUE)
```



## Prepare dataset
### 1. Mutate and filter raw BOLD dataset

Filter and mutate georeferenced sequence dataset to produce a curated dataframe with rows as individual specimen and columns as specimen information. It adds a new column sequence with DNA sequences as string.

The function prepare_bold_res apply 5 filters :

* Select specimen with given marker_code
* Remove specimen with no species_name information
* Remove specimen with no lat or lon coordinates information
* Remove specimen with IUAPC ambiguities on DNA sequences
* Select specimen with DNA sequences within a given range of lengths in bp

```{r}
## filter and mutate
prparedResBold <- prepare_bold_res(resBold,
                                   marker_code="COI-5P",
                                   species_names=TRUE, 
                                   coordinates=TRUE, 
                                   ambiguities=TRUE, 
                                   min_length=420,
                                   max_length=720
                                  )
```

