---
title: "Spatial studies of genetic diversity within species"
author: "Pierre-Edouard GUERIN, Stephanie MANEL, EPHE, CNRS"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{map_marine}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---



## Prerequisites

```{r setup}
library(rgeogendiv)
```




## BOLD dataset

**BOLD** (Barcode Of Life Database) is a database of Barcode DNA sequences of georeferenced specimen that closely approximate species.

We use the package `bold` to download a set of georeferenced sequences for the *Pomacanthidae* taxon order request.

```{r}
library(bold)
taxonRequest <- "Pomacanthidae"
resBold <- bold::bold_seqspec(taxon=taxonRequest, sepfasta=TRUE)
```



## Prepare dataset
### 1. Mutate and filter raw BOLD dataset

Filter and mutate georeferenced sequence dataset to produce a curated dataframe with rows as individual specimen and columns as specimen information. It adds a new column sequence with DNA sequences as string.

The function prepare_bold_res apply 5 filters :

* Select specimen with given marker_code
* Remove specimen with no species_name information
* Remove specimen with no lat or lon coordinates information
* Remove specimen with IUAPC ambiguities on DNA sequences
* Select specimen with DNA sequences within a given range of lengths in bp

```{r}
## filter and mutate
predResBold <- prepare_bold_res(resBold,
                                   marker_code="COI-5P",
                                   species_names=TRUE, 
                                   coordinates=TRUE, 
                                   ambiguities=TRUE, 
                                   min_length=420,
                                   max_length=720
                                  )
```


### 2. Verify species names with FishBase

As we work on fishes and later with Reef Life Survey dataset, we search for synonyms into FishBase to verify species names from the BOLD dataset.

The function `fishbase_verify_bold_species` checks species_name field and seek for FishBase synonyms. Then it adds a new field 'fishbase_species_name'.

```{r}
## validate species names
predResBold.verified <- fishbase_verify_bold_species(prparedResBold)
```



